---
title: "Untitled"
output: html_document
---

```{r,message=FALSE}
setwd("~/Desktop/airbnbhost/data")
load("../data/processed_listings.RData")
library(topicmodels)
library(tm)
library(tidytext)
library(tidyverse)

```

```{r}
#remove those words which appear all frequently in description
word = c("manhattan","brooklyn","queens","staten","island","bronx","apartment","bedroom","kitchen")
data("stop_words")
stop_words <- stop_words %>%
  bind_rows(mutate(tibble(word), lexicon = "updated"))
man = subset(data,neighbourhood_group == "Manhattan") %>%
  unnest_tokens(word,stemmedwords) %>%
  anti_join(stop_words)
brook = subset(data,neighbourhood_group == "Brooklyn") %>%
  unnest_tokens(word,stemmedwords)%>%
  anti_join(stop_words)
queens = subset(data,neighbourhood_group == "Queens") %>%
  unnest_tokens(word,stemmedwords)%>%
  anti_join(stop_words)
si = subset(data,neighbourhood_group == "Staten Island") %>%
  unnest_tokens(word,stemmedwords)%>%
  anti_join(stop_words)
bronx = subset(data,neighbourhood_group == "Bronx") %>%
  unnest_tokens(word,stemmedwords)%>%
  anti_join(stop_words)


par(mfrow=c(3,3))

#man %>% group_by(word) %>% summarise(n=n()) %>% arrange(desc(n))
#brook %>% group_by(word) %>% summarise(n=n()) %>% arrange(desc(n))



man %>%
  count(word, sort = TRUE) %>%
  filter(n >10000) %>%
  mutate(word = reorder(word, n))%>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()+
  ggtitle("description of Manhattan airbnb") +
  theme(plot.title = element_text(size = 10))+
  theme(plot.margin = margin(1,3,1,3,"cm"))

brook %>%
  count(word, sort = TRUE) %>%
  filter(n > 10000) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()+
  ggtitle("description of Brooklyn airbnb") +
  theme(plot.title = element_text(size = 10))+
  theme(plot.margin = margin(1,3,1,3,"cm"))

queens%>%
  count(word, sort = TRUE) %>%
  filter(n > 3500) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()+
  ggtitle("description of Queens airbnb") +
  theme(plot.title = element_text(size = 10))+
  theme(plot.margin = margin(1,3,1,3,"cm"))

si%>%
  count(word, sort = TRUE) %>%
  filter(n > 300) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()+
  ggtitle("description of Staten Island airbnb") +
  theme(plot.title = element_text(size = 10))+
  theme(plot.margin = margin(1,3,1,3,"cm"))

bronx%>%
  count(word, sort = TRUE) %>%
  filter(n >600) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()+
  ggtitle("description of Bronx airbnb") +
  theme(plot.title = element_text(size = 10))+
  theme(plot.margin = margin(1,3,1,3,"cm"))


```
the top words used frequently in the description 
for Manhattan:apartment, bedroom, located, walk,kitchen
for Brooklyn: apartment, bedroom,kitchen,train,living
for Queens:apartment,minutes, bedroom,min,train,kitchen
for Staten Island:ferry,private,house,walk,minutes
for Bronx: train,apartment,guests,mintues,walk


after removing some top common words:
for Manhattan:located,walk,park,bed,living
for Brooklyn: train,living,walk,minutes,bed
for Queens:minutes, min,train,walk,bed
for Staten Island:ferry,private,house,walk,minutes
for Bronx: train,guests,minutes,walk,private


